Covariate and differential expression analysis of ROSMAP reprocessed counts

### 2019-09-17 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synapseLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20798012")
```

>>>>

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20798012")
```

### 2019-09-17 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synapseLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20798012")
```

>>>>

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20798012")
```

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synapseLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20800296")
```

>>>>

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synLogin()
knit2synapse::knitfile2synapse(file = "~/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd", 
                               owner = "syn20800296")
```
